Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-14 MS_revised.tex
comment 28

Lineages in the diverse family Satyrinae radiated simultaneously with
the radiation of their main hostplant, grasses, during the climatic
cooling in the Oligocene \cite{pena2008}. Thus, it is somewhat surprising that
part of Satyrinae were found to have accelerated diversification in only
13\% of the trees from the posterior distribution. Although this can be
attributed to low phylogenetic signal \cite{wahlberg2009}, the clade Satyrini is
very robust \cite{wahlberg2009} and MEDUSA failed to identify any significant
accelerated net diversification rate for Satyrini. It appears that the
radiation of Satyrini as a whole was not remarkably fast and therefore
not picked up by MEDUSA, although it estimated a diversification shift
for Satyrini + its sister clade. This should be expected if the
diversification of Satyrini occurred in a stepwise manner, with pulses
or bursts of diversification for certain lineages but unlikely for the
tribe Satyrini as a whole.

>>>>

Lineages in the diverse family Satyrinae radiated simultaneously with
the radiation of their main hostplant, grasses, during the climatic
cooling in the Oligocene \cite{pena2008}. Thus, it is somewhat surprising that
part of Satyrinae were found to have accelerated diversification in only
13\% of the trees from the posterior distribution. Although this can be
attributed to low phylogenetic signal \cite{wahlberg2009}, the clade Satyrini is
very robust \cite{wahlberg2009} and MEDUSA failed to identify any significant
accelerated net diversification rate for Satyrini.
It appears that the
radiation of Satyrini as a whole was not remarkably fast and therefore
not detected by MEDUSA, although it estimated a diversification shift
for Satyrini + its sister clade. This should be expected if the
diversification of Satyrini occurred in a stepwise manner, with pulses
or bursts of diversification for certain lineages but unlikely for the
tribe Satyrini as a whole.
